Bioconductor workflow for single-cell RNA sequencing: Normalization, dimensionality reduction, clustering, and lineage inference

### 2018-08-13 workflow/workflow.Rmd
Changes

```{r zinb,eval=TRUE}
print(system.time(dataObj <- zinbwave(dataObj, K = 10, X = "~ Batch",
                                      residuals = TRUE, 
                                      normalizedValues = TRUE)))
```

```{r}
save(dataObj, file= 'dataObj_afterZinbwave_k10.rda')
#load('dataObj_afterZinbwave.rda')
```

@@

```{r}
fit <- readRDS("fit_allK.rds")
plot(k_values, sapply(fit, zinbBIC, t(counts(dataObj))), 
     ylab = "BIC", xlab = "K", type = "b")
plot(k_values, sapply(fit, zinbAIC, t(counts(dataObj))),
     ylab = "AIC", xlab = "K", type = "b")
```

>>>>

```{r zinb,eval=FALSE}
print(system.time(dataObj <- zinbwave(dataObj, K = 10, X = "~ Batch",
                                      residuals = TRUE, 
                                      normalizedValues = TRUE)))
```

```{r}
#save(dataObj, file= 'dataObj_afterZinbwave_k10.rda')
load('dataObj_afterZinbwave_k10.rda')
```

@@

```{r}
k_values <- c(1: 5, 10)
fit <- readRDS("fit_allK.rds")
plot(k_values, sapply(fit, zinbBIC, t(counts(dataObj))), 
     ylab = "BIC", xlab = "K", type = "b")
plot(k_values, sapply(fit, zinbAIC, t(counts(dataObj))),
     ylab = "AIC", xlab = "K", type = "b")
```
